### 2015-06-01 writing/SNLI paper/entailment_eval.tex
A tiny bit more storytelling.

The results are shown in \reftab{tab:transferresults}. Training on SICK alone yields poor performance, and the model trained on our data alone fails dramatically by labeling more \ii{neutral} examples as \ii{contradiction}s than correctly. Transferring representations, in contrast, yields the best performance yet reported on SICK for an unaugmented neural network model, surpasses the available EOP models, and approaches both the overall state of the art at 84.6\% \cite{lai2014illinois} and the 84\% level of interannotator agreement, which likely represents an approximate performance ceiling. This suggests that the introduction of a large high-quality corpus makes it  possible to train representation-learning models for sentence meaning that are competitive with the best hand-engineered models on inference tasks.

We attempted to apply this same transfer evaluation technique to the RTE-3 challenge, but found that the small size of the training set (800 examples) did not allow the model to adapt to the unfamiliar genre of text used in that corpus, such that neither our transfer model nor our randomly initialized model reached competitive performance.
Further research on effective transfer learning on small data sets with neural models might facilitate improvements here.

>>>>

The results are shown in \reftab{tab:transferresults}. Training on SICK alone yields poor performance, and the model trained on our data misunderstands the subtly different meanings of the (identically named) SICK labels, labeling more \ii{neutral} examples as \ii{contradiction}s than correctly. Transferring representations, in contrast, yields the best performance yet reported on SICK for an unaugmented neural network model, surpasses the available EOP models, and approaches both the overall state of the art at 84.6\% \cite{lai2014illinois} and the 84\% level of interannotator agreement, which likely represents an approximate performance ceiling. This suggests that the introduction of a large high-quality corpus makes it  possible to train representation-learning models for sentence meaning that are competitive with the best hand-engineered models on inference tasks.

We attempted to apply this same transfer evaluation technique to the RTE-3 challenge, but found that the small training set (800 examples) did not allow the model to adapt to the unfamiliar genre of text used in that corpus, such that no training configuration yielded competitive performance.
Further research on effective transfer learning on small data sets with neural models might facilitate improvements here.
